### 2021-07-14 msc dissertation code.Rmd
main code

---
title: "msc dissertation"
author: "Halleyson Li"
date: "14/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-07-14 msc dissertation code.Rmd
data

@@
 author: "Halleyson Li"
-date: "14/07/2021"
+date: "'r Sys.Date()'"
 output: html_document
+line-citations: apalike
+linkcolor: blue
+frontsize: 12pt
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+\newpage
+
+# *Notes*{-}
+1. The GitHub repository for this project could access through [here](https://github.com/halleyson/msc-dissertation.git)
+
+# Loading data
+
+```{r, message=FALSE}
+
+library(readr)
+
+pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
+Pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
+
 ```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-07-19 msc dissertation code.Rmd
latest

@@
 pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
-Pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
+pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
+# Quick check
+head(pennycook2)
 
 ```
+
+# General steps to regenerate headline result (study 2)
+## data cleaning
+
+```{r, message=FALSE}
+
+# rename columns that contains special characters
+colnames(pennycook2)
+names(pennycook2)[1] <- "condition"
+
+#conclude a sheet with only the relevant information 
+#condition 1 = control; condition 2 = treatment
+
+#Choose with the column position 
+library("dplyr")
+pennystudy2r1 <- pennycook2 %>% 
+  select (c(1, 2, 3, 4, 57, 60, 250, 252, 284))
+
+#re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
+pennystudy2r1$Fake[pennystudy2r1$Fake > 0 & pennystudy2r1$Fake < 4] <- 0
+pennystudy2r1$Fake[pennystudy2r1$Fake > 3 & pennystudy2r1$Fake < 7] <- 1
+pennystudy2r1$Fake
+
+pennystudy2r1$Real[pennystudy2r1$Real > 0 & pennystudy2r1$Real < 4] <- 0
+pennystudy2r1$Real[pennystudy2r1$Real > 3 & pennystudy2r1$Real < 7] <- 1
+pennystudy2r1$Real
+
+```
+## reproduction of results (interaction between headline veracity and treatment)
+### without considering attention check
+```{r, message=FALSE}
+
+lm1 = lm(Discern ~ condition, data = pennystudy2r1)
+summary(lm1)
+
+```
+
+### reproduction of figure 2 without considering attention check
+
+```{r, message=FALSE}
+pennystudy2r1$screen3_2
+
+library(ggplot2)
+
+pennystudy2plot1 <- pennystudy2r1 %>% 
+  select (c(1, 2, 3))
+
+library(reshape2)
+
+pennystudy2plot1 <- melt(pennystudy2plot1, id = 'condition')
+head(pennystudy2plot1)
+
+#Find out the sum for each type of news in different condition
+p1 <- aggregate(value~condition+variable, data = pennystudy2plot1, FUN = sum)
+
+ggplot(p1, aes(x = condition, y = value / 428, fill = variable)) + 
+  geom_bar(stat = 'identity',position = 'dodge')
+
+```

### 2021-07-19 msc dissertation code.Rmd
Add files via upload

@@
 
+#create veracity column (Real - Fake)
+pennystudy2r1['veracity']=pennystudy2r1['Real'] - pennystudy2r1['Fake']
+
+#successful screen1 test (result = 2)
+pennystudy2r1['screen1']=pennystudy2r1['screen1_4'] + pennystudy2r1['screen1_7']
+
+#successful screen2 test (result = 2)
+pennystudy2r1['screen2']=pennystudy2r1['screen2_3'] + pennystudy2r1['screen2_5']
+
+#successful screen3 test (result = 3)
+pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3_2,1)
+pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,2)
+pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,4)
+pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,5)
+#to check if screen 3 successful
+mean(pennystudy2r1$screen3, na.rm = TRUE)
+
+#replace 2 and 3 to 1
+pennystudy2r1["screen1"][pennystudy2r1["screen1"] == 2] <- 1
+pennystudy2r1["screen2"][pennystudy2r1["screen2"] == 2] <- 1
+pennystudy2r1["screen3"][pennystudy2r1["screen3"] == 3] <- 1
+
 ```
+
 ## reproduction of results (interaction between headline veracity and treatment)
@@
 ```{r, message=FALSE}
+install.packages("sandwich") 
+install.packages("stargazer")
+install.packages("lmtest")
+library(lmtest)
+library(stargazer) 
+library(sandwich)
 
-lm1 = lm(Discern ~ condition, data = pennystudy2r1)
+lm1 <- lm(Discern ~ condition + veracity + veracity*condition, data = pennystudy2r1)
+summary(lm1)
+
+stargazer(lm1, type='text')
+
+coeftest(lm1, vcovHC)
+
+#z scored
+scale(pennystudy2r1$Discern)
+
+lm1 = lm(scale(pennystudy2r1$Discern) ~ condition, data = pennystudy2r1)
 summary(lm1)

### 2021-07-20 msc dissertation code.Rmd
new
newest

@@
 
+#replace condition control = 0 treatment = 1
+pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
+pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1
+
 ```
@@
 
-lm1 <- lm(Discern ~ condition + veracity + veracity*condition, data = pennystudy2r1)
+lm1 <- lm(Discern ~ Real + Real*condition, data = pennystudy2r1)
 summary(lm1)

### 2021-07-20 msc dissertation code.Rmd
latest

@@
 
-#replace condition control = 0 treatment = 1
+#re-code condition control = 0 treatment = 1
 pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0

### 2021-07-20 msc dissertation code.Rmd
latest

@@
 pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,5)
-#to check if screen 3 successful
+#check if screen 3 successful
 mean(pennystudy2r1$screen3, na.rm = TRUE)
 
-#replace 2 and 3 to 1
+#re-code screen test: replace 2 and 3 to 1
 pennystudy2r1["screen1"][pennystudy2r1["screen1"] == 2] <- 1

### 2021-08-02 msc dissertation code.Rmd
latest

@@
 
+#replace NA to 0 in screen 1,2,3
+
+pennystudy2r1[c("screen1","screen2","screen3")][is.na(pennystudy2r1[c("screen1","screen2","screen3")])] <- 0
+
+#create dummy column, add screen 1,2,3 together. Screen = 3 indicate success in all attention check
+pennystudy2r1['dummycheck']=pennystudy2r1['screen1'] + pennystudy2r1['screen2'] + pennystudy2r1['screen3']
+
+#like the researcher did, change data frame from wide to long
+##first drop unnecessary column
+pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,10,14))
+
+##Add ID column
+pennys2r1long <- tibble::rowid_to_column(pennys2r1long, "ID")
+
+## change from wide to long
+library(tidyr)
+
+keycol <- "newstype"
+valuecol <- "measurement"
+gathercols <- c("Fake","Real")
+
+pennys2r1long <- gather_(pennys2r1long, keycol, valuecol, gathercols)
+
+##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one
+
+merge(pennystudy2r1, pennys2r1long, by.x='condition', by.y='ID')
+
+##organize data by ID, then reorder the column
+pennys2r1long <- pennys2r1long[order(pennys2r1long$ID),]
+
+pennys2r1long <- pennys2r1long[, c(1, 2, 6, 7, 4, 5, 3)]
+
+##separating the data based on number of successful attention check
+
+### attention check above and equal to 1
+pennys2r1longa1 <- subset(pennys2r1long, dummycheck %in% c("1","2","3"))
+
+### attention check above and equal to 2
+pennys2r1longa2 <- subset(pennys2r1long, dummycheck %in% c("2","3"))
+
+### attention check equal to 3
+pennys2r1longa3 <- subset(pennys2r1long, dummycheck %in% c("3"))
+
 ```
@@
 
-lm1 <- lm(Discern ~ Real + Real*condition, data = pennystudy2r1)
+lm1 <- lm(veracity ~ newstype + newstype*condition, data = pennys2r1longa2)
 summary(lm1)
@@
 
-lm1 = lm(scale(pennystudy2r1$Discern) ~ condition, data = pennystudy2r1)
-summary(lm1)
+install.packages("effectsize")
+library(effectsize)
+
+cohens_d(pennystudy2r1)
 
@@
 
+### graph 1: including all
 ```{r, message=FALSE}
-pennystudy2r1$screen3_2
 
@@
 
-pennystudy2plot1 <- pennystudy2r1 %>%
-  select (c(1, 2, 3))
+#Since the plot not specify which condition they use, then I need to plot all 4 graph in different condition
 
-library(reshape2)
+#condition 1: all
 
-pennystudy2plot1 <- melt(pennystudy2plot1, id = 'condition')
-head(pennystudy2plot1)
+pennystudy2plot1 <- pennys2r1long %>%
+  select (c(1, 2, 3, 4))
 
 #Find out the sum for each type of news in different condition
-p1 <- aggregate(value~condition+variable, data = pennystudy2plot1, FUN = sum)
+p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, FUN = sum)
 
-ggplot(p1, aes(x = condition, y = value / 428, fill = variable)) + 
-  geom_bar(stat = 'identity',position = 'dodge')
+##double check for correctness
+sum(pennystudy2plot1$measurement,na.rm = TRUE)
 
+#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
+ggplot(p1, aes(x = condition, y = measurement/428, fill = newstype)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
+    scale_y_continuous(labels = scales::percent)
 ```
+### graph 2 attention check above and equal to 1
+
+```{r, message=FALSE}
+
+#condition 2: above and equal to 1
+
+pennystudy2plot2 <- pennys2r1longa1 %>%
+  select (c(1, 2, 3, 4))
+
+#Find out the sum for each type of news in different condition
+p2 <- aggregate(measurement~condition+newstype, data = pennystudy2plot2, FUN = sum)
+
+##double check for correctness
+sum(pennystudy2plot2$measurement,na.rm = TRUE)
+
+#since the obs is 1664, thus 1664/2 = 832 participants. So to get percentage of sharing intention each fake and real news need to divided by 832/2 = 416
+ggplot(p2, aes(x = condition, y = measurement/416, fill = newstype)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = round(measurement/416, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
+    scale_y_continuous(labels = scales::percent)
+```
+
+### graph 3 attention check above and equal to 2
+```{r, message=FALSE}
+#condition 3: above and equal to 2
+pennystudy2plot3 <- pennys2r1longa2 %>%
+  select (c(1, 2, 3, 4))
+
+#Find out the sum for each type of news in different condition
+p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, FUN = sum)
+
+##double check for correctness
+sum(pennystudy2plot3$measurement,na.rm = TRUE)
+
+#since the obs is 1292 for attention > 2, thus 1292/2 = 646 participants. So to get percentage of sharing intention each fake and real news need to divided by 646/2 = 323
+ggplot(p3, aes(x = condition, y = measurement/323, fill = newstype)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = round(measurement/323, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
+    scale_y_continuous(labels = scales::percent)
+```
+
+### graph 4 attention check equal to 3
+```{r, message=FALSE}
+#condition 3: equal to 3
+pennystudy2plot4 <- pennys2r1longa3 %>%
+  select (c(1, 2, 3, 4))
+
+#Find out the sum for each type of news in different condition
+p4 <- aggregate(measurement~condition+newstype, data = pennystudy2plot4, FUN = sum)
+
+##double check
+sum(pennystudy2plot4$measurement,na.rm = TRUE)
+
+#since the obs is 460 for attention = 3, thus 460/2 = 230 participants. So to get percentage of sharing intention each fake and real news need to divided by 230/2 = 115
+ggplot(p4, aes(x = condition, y = measurement/115, fill = newstype)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = round(measurement/115, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
+    scale_y_continuous(labels = scales::percent)
+```

### 2021-08-04 msc dissertation code.Rmd
latest

@@
 
-install.packages("effectsize")
-library(effectsize)
+#calculate the effect size cohen's d
+##since they need to compare true vs false headline in different condition, thus, create a new data frame that only contain treatment and control with the attention check above and equal to 2, as stated in the research
 
-cohens_d(pennystudy2r1)
+install.packages("effsize")
+library(effsize)
+
+pennys2r1a2cohen <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
+pennys2r1a2cohenc <- subset(pennys2r1a2cohen, condition %in% c("0"))
+pennys2r1a2cohent <- subset(pennys2r1a2cohen, condition %in% c("1"))
+
+cohen.d(pennys2r1a2cohenc$Fake, pennys2r1a2cohenc$Real, na.rm = TRUE)
+cohen.d(pennys2r1a2cohent$Fake, pennys2r1a2cohent$Real, na.rm = TRUE)
+
+#condition vs measurement
+
+pennys2r1a2cohenc <- subset(pennys2r1longa2, condition %in% c("0"))
+pennys2r1a2cohent <- subset(pennys2r1longa2, condition %in% c("1"))
+
+cohen.d(pennys2r1a2cohenc$condition, pennys2r1a2cohenc$measurement, na.rm = TRUE)
+cohen.d(pennys2r1a2cohent$condition, pennys2r1a2cohent$measurement, na.rm = TRUE)
 
@@
 #Find out the sum for each type of news in different condition
-p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, FUN = sum)
+
+p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, na.rm = TRUE, FUN = sum)
+p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))
 
@@
 #since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
-ggplot(p1, aes(x = condition, y = measurement/428, fill = newstype)) + 
+ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
   geom_bar(stat = 'identity',position = 'dodge') + 
   geom_text(
-    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
-    scale_y_continuous(labels = scales::percent)
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
 ```
@@
 
+#separating the sheet
+
+pennystudy2plot2c <- subset(pennystudy2plot2, condition %in% c("0"))
+pennystudy2plot2t <- subset(pennystudy2plot2, condition %in% c("1"))
+
 #Find out the sum for each type of news in different condition
@@
 #since the obs is 1664, thus 1664/2 = 832 participants. So to get percentage of sharing intention each fake and real news need to divided by 832/2 = 416
-ggplot(p2, aes(x = condition, y = measurement/416, fill = newstype)) + 
+ggplot(p2, aes(x = condition, y = measurement/428, fill = newstype)) + 
   geom_bar(stat = 'identity',position = 'dodge') + 
   geom_text(
-    aes(label = round(measurement/416, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
+    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
     scale_y_continuous(labels = scales::percent)
@@
 #Find out the sum for each type of news in different condition
-p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, FUN = sum)
+
+p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, na.rm = TRUE, FUN = sum)
+p3 <- transform(p3, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))
 
@@
 
-#since the obs is 1292 for attention > 2, thus 1292/2 = 646 participants. So to get percentage of sharing intention each fake and real news need to divided by 646/2 = 323
-ggplot(p3, aes(x = condition, y = measurement/323, fill = newstype)) + 
+#plot the graph under the proportion of overall observation (856)
+ggplot(p3, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
   geom_bar(stat = 'identity',position = 'dodge') + 
   geom_text(
-    aes(label = round(measurement/323, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
-    scale_y_continuous(labels = scales::percent)
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
+```
+### graph 3 attention check above and equal to 2: mean
+```{r, message=FALSE}
+#condition 3: above and equal to 2
+pennystudy2plot3 <- pennys2r1longa2 %>%
+  select (c(1, 2, 3, 4))
+
+pennystudy2plot3c <- subset(pennystudy2plot3, condition %in% c("0"))
+pennystudy2plot3t <- subset(pennystudy2plot3, condition %in% c("1"))
+
+#Find out the sum and percentage for each type of news in each condition
+
+##control, percentage = 658/2 = 329
+p31 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3c, na.rm = TRUE, FUN = sum)
+p31 <- transform(p31, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/329, 4)*100)))
+
+##treatment, percentage = 634/2 = 317
+p32 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3t, na.rm = TRUE, FUN = sum)
+p32 <- transform(p32, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/317, 4)*100)))
+
+#merge two table together under same column name
+p3 <- rbind(p31,p32)
+
+##double check for correctness
+sum(pennystudy2plot3$measurement,na.rm = TRUE)
+
+#plot the graph
+ggplot(p3, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
 ```

### 2021-08-04 msc dissertation code.Rmd
latest

@@
 
-#conclude a sheet with only the relevant information 
-#condition 1 = control; condition 2 = treatment
+#remove a participants that did not answer or fail to record any questions
+
+pennycook2 <- pennycook2[!is.na(pennycook2$Fake),]
+
+#data description: condition 1 = control; condition 2 = treatment
 
@@
 pennystudy2r1 <- pennycook2 %>% 
-  select (c(1, 2, 3, 4, 57, 60, 250, 252, 284))
+  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
 
 #re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
+
+##Fake
 pennystudy2r1$Fake[pennystudy2r1$Fake > 0 & pennystudy2r1$Fake < 4] <- 0
@@
 
+pennystudy2r1$Fake1_1[pennystudy2r1$Fake1_1 > 0 & pennystudy2r1$Fake1_1 < 4] <- 0
+pennystudy2r1$Fake1_1[pennystudy2r1$Fake1_1 > 3 & pennystudy2r1$Fake1_1 < 7] <- 1
+
+pennystudy2r1$Fake1_2[pennystudy2r1$Fake1_2 > 0 & pennystudy2r1$Fake1_2 < 4] <- 0
+pennystudy2r1$Fake1_2[pennystudy2r1$Fake1_2 > 3 & pennystudy2r1$Fake1_2 < 7] <- 1
+
+pennystudy2r1$Fake1_3[pennystudy2r1$Fake1_3 > 0 & pennystudy2r1$Fake1_3 < 4] <- 0
+pennystudy2r1$Fake1_3[pennystudy2r1$Fake1_3 > 3 & pennystudy2r1$Fake1_3 < 7] <- 1
+
+pennystudy2r1$Fake1_4[pennystudy2r1$Fake1_4 > 0 & pennystudy2r1$Fake1_4 < 4] <- 0
+pennystudy2r1$Fake1_4[pennystudy2r1$Fake1_4 > 3 & pennystudy2r1$Fake1_4 < 7] <- 1
+
+pennystudy2r1$Fake1_5[pennystudy2r1$Fake1_5 > 0 & pennystudy2r1$Fake1_5 < 4] <- 0
+pennystudy2r1$Fake1_5[pennystudy2r1$Fake1_5 > 3 & pennystudy2r1$Fake1_5 < 7] <- 1
+
+pennystudy2r1$Fake1_6[pennystudy2r1$Fake1_6 > 0 & pennystudy2r1$Fake1_6 < 4] <- 0
+pennystudy2r1$Fake1_6[pennystudy2r1$Fake1_6 > 3 & pennystudy2r1$Fake1_6 < 7] <- 1
+
+pennystudy2r1$Fake1_7[pennystudy2r1$Fake1_7 > 0 & pennystudy2r1$Fake1_7 < 4] <- 0
+pennystudy2r1$Fake1_7[pennystudy2r1$Fake1_7 > 3 & pennystudy2r1$Fake1_7 < 7] <- 1
+
+pennystudy2r1$Fake1_8[pennystudy2r1$Fake1_8 > 0 & pennystudy2r1$Fake1_8 < 4] <- 0
+pennystudy2r1$Fake1_8[pennystudy2r1$Fake1_8 > 3 & pennystudy2r1$Fake1_8 < 7] <- 1
+
+pennystudy2r1$Fake1_9[pennystudy2r1$Fake1_9 > 0 & pennystudy2r1$Fake1_9 < 4] <- 0
+pennystudy2r1$Fake1_9[pennystudy2r1$Fake1_9 > 3 & pennystudy2r1$Fake1_9 < 7] <- 1
+
+pennystudy2r1$Fake1_10[pennystudy2r1$Fake1_10 > 0 & pennystudy2r1$Fake1_10 < 4] <- 0
+pennystudy2r1$Fake1_10[pennystudy2r1$Fake1_10 > 3 & pennystudy2r1$Fake1_10 < 7] <- 1
+
+pennystudy2r1$Fake1_11[pennystudy2r1$Fake1_11 > 0 & pennystudy2r1$Fake1_11 < 4] <- 0
+pennystudy2r1$Fake1_11[pennystudy2r1$Fake1_11 > 3 & pennystudy2r1$Fake1_11 < 7] <- 1
+
+pennystudy2r1$Fake1_12[pennystudy2r1$Fake1_12 > 0 & pennystudy2r1$Fake1_12 < 4] <- 0
+pennystudy2r1$Fake1_12[pennystudy2r1$Fake1_12 > 3 & pennystudy2r1$Fake1_12 < 7] <- 1
+
+pennystudy2r1$Fake1_13[pennystudy2r1$Fake1_13 > 0 & pennystudy2r1$Fake1_13 < 4] <- 0
+pennystudy2r1$Fake1_13[pennystudy2r1$Fake1_13 > 3 & pennystudy2r1$Fake1_13 < 7] <- 1
+
+pennystudy2r1$Fake1_14[pennystudy2r1$Fake1_14 > 0 & pennystudy2r1$Fake1_14 < 4] <- 0
+pennystudy2r1$Fake1_14[pennystudy2r1$Fake1_14 > 3 & pennystudy2r1$Fake1_14 < 7] <- 1
+
+pennystudy2r1$Fake1_15[pennystudy2r1$Fake1_15 > 0 & pennystudy2r1$Fake1_15 < 4] <- 0
+pennystudy2r1$Fake1_15[pennystudy2r1$Fake1_15 > 3 & pennystudy2r1$Fake1_15 < 7] <- 1
+
+##Real
 pennystudy2r1$Real[pennystudy2r1$Real > 0 & pennystudy2r1$Real < 4] <- 0
@@
 pennystudy2r1$Real
+
+pennystudy2r1$Real1_1[pennystudy2r1$Real1_1 > 0 & pennystudy2r1$Real1_1 < 4] <- 0
+pennystudy2r1$Real1_1[pennystudy2r1$Real1_1 > 3 & pennystudy2r1$Real1_1 < 7] <- 1
+
+pennystudy2r1$Real1_2[pennystudy2r1$Real1_2 > 0 & pennystudy2r1$Real1_2 < 4] <- 0
+pennystudy2r1$Real1_2[pennystudy2r1$Real1_2 > 3 & pennystudy2r1$Real1_2 < 7] <- 1
+
+pennystudy2r1$Real1_3[pennystudy2r1$Real1_3 > 0 & pennystudy2r1$Real1_3 < 4] <- 0
+pennystudy2r1$Real1_3[pennystudy2r1$Real1_3 > 3 & pennystudy2r1$Real1_3 < 7] <- 1
+
+pennystudy2r1$Real1_4[pennystudy2r1$Real1_4 > 0 & pennystudy2r1$Real1_4 < 4] <- 0
+pennystudy2r1$Real1_4[pennystudy2r1$Real1_4 > 3 & pennystudy2r1$Real1_4 < 7] <- 1
+
+pennystudy2r1$Real1_5[pennystudy2r1$Real1_5 > 0 & pennystudy2r1$Real1_5 < 4] <- 0
+pennystudy2r1$Real1_5[pennystudy2r1$Real1_5 > 3 & pennystudy2r1$Real1_5 < 7] <- 1
+
+pennystudy2r1$Real1_6[pennystudy2r1$Real1_6 > 0 & pennystudy2r1$Real1_6 < 4] <- 0
+pennystudy2r1$Real1_6[pennystudy2r1$Real1_6 > 3 & pennystudy2r1$Real1_6 < 7] <- 1
+
+pennystudy2r1$Real1_7[pennystudy2r1$Real1_7 > 0 & pennystudy2r1$Real1_7 < 4] <- 0
+pennystudy2r1$Real1_7[pennystudy2r1$Real1_7 > 3 & pennystudy2r1$Real1_7 < 7] <- 1
+
+pennystudy2r1$Real1_8[pennystudy2r1$Real1_8 > 0 & pennystudy2r1$Real1_8 < 4] <- 0
+pennystudy2r1$Real1_8[pennystudy2r1$Real1_8 > 3 & pennystudy2r1$Real1_8 < 7] <- 1
+
+pennystudy2r1$Real1_9[pennystudy2r1$Real1_9 > 0 & pennystudy2r1$Real1_9 < 4] <- 0
+pennystudy2r1$Real1_9[pennystudy2r1$Real1_9 > 3 & pennystudy2r1$Real1_9 < 7] <- 1
+
+pennystudy2r1$Real1_10[pennystudy2r1$Real1_10 > 0 & pennystudy2r1$Real1_10 < 4] <- 0
+pennystudy2r1$Real1_10[pennystudy2r1$Real1_10 > 3 & pennystudy2r1$Real1_10 < 7] <- 1
+
+pennystudy2r1$Real1_11[pennystudy2r1$Real1_11 > 0 & pennystudy2r1$Real1_11 < 4] <- 0
+pennystudy2r1$Real1_11[pennystudy2r1$Real1_11 > 3 & pennystudy2r1$Real1_11 < 7] <- 1
+
+pennystudy2r1$Real1_12[pennystudy2r1$Real1_12 > 0 & pennystudy2r1$Real1_12 < 4] <- 0
+pennystudy2r1$Real1_12[pennystudy2r1$Real1_12 > 3 & pennystudy2r1$Real1_12 < 7] <- 1
+
+pennystudy2r1$Real1_13[pennystudy2r1$Real1_13 > 0 & pennystudy2r1$Real1_13 < 4] <- 0
+pennystudy2r1$Real1_13[pennystudy2r1$Real1_13 > 3 & pennystudy2r1$Real1_13 < 7] <- 1
+
+pennystudy2r1$Real1_14[pennystudy2r1$Real1_14 > 0 & pennystudy2r1$Real1_14 < 4] <- 0
+pennystudy2r1$Real1_14[pennystudy2r1$Real1_14 > 3 & pennystudy2r1$Real1_14 < 7] <- 1
+
+pennystudy2r1$Real1_15[pennystudy2r1$Real1_15 > 0 & pennystudy2r1$Real1_15 < 4] <- 0
+pennystudy2r1$Real1_15[pennystudy2r1$Real1_15 > 3 & pennystudy2r1$Real1_15 < 7] <- 1
 
@@
 ##first drop unnecessary column
-pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,10,14))
+colnames(pennystudy2r1)
+
+pennys2r1long <- subset(pennystudy2r1, select = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,40,44))
 
@@
 valuecol <- "measurement"
-gathercols <- c("Fake","Real")
+gathercols <- c("Fake1_1","Fake1_2","Fake1_3","Fake1_4","Fake1_5","Fake1_6","Fake1_7","Fake1_8","Fake1_9","Fake1_10","Fake1_11","Fake1_12","Fake1_13","Fake1_14","Fake1_15","Real1_1","Real1_2","Real1_3","Real1_4","Real1_5","Real1_6","Real1_7","Real1_8","Real1_9","Real1_10","Real1_11","Real1_12","Real1_13","Real1_14","Real1_15")
 
@@
 
-pennys2r1long <- pennys2r1long[, c(1, 2, 6, 7, 4, 5, 3)]
+pennys2r1long <- pennys2r1long[, c(1, 2, 8, 9, 7, 4, 3, 6, 5)]
+
+##rename real and fake to avereal and avefake, change dummycheck to attentioncheck to make it clear
+
+names(pennys2r1long)[6] <- "Real_ave"
+names(pennys2r1long)[7] <- "Fake_ave"
+names(pennys2r1long)[5] <- "attentioncheck"
+
+##create a headline veracity column, fake news items code as 0, real news items code as 1
+
+pennys2r1long <- pennys2r1long %>%
+  mutate(headlineveracity = case_when(
+    startsWith(newstype, "R") ~ "1",
+    startsWith(newstype, "F") ~ "0"
+    ))
+
+##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627
+
+pennys2r1long_nona <- pennys2r1long[!is.na(pennys2r1long$measurement),]
 
@@
 ### attention check above and equal to 1
-pennys2r1longa1 <- subset(pennys2r1long, dummycheck %in% c("1","2","3"))
+pennys2r1longa1 <- subset(pennys2r1long, attentioncheck %in% c("1","2","3"))
 
 ### attention check above and equal to 2
-pennys2r1longa2 <- subset(pennys2r1long, dummycheck %in% c("2","3"))
+pennys2r1longa2 <- subset(pennys2r1long, attentioncheck %in% c("2","3"))
 
 ### attention check equal to 3
-pennys2r1longa3 <- subset(pennys2r1long, dummycheck %in% c("3"))
+pennys2r1longa3 <- subset(pennys2r1long, attentioncheck %in% c("3"))
 
+###find out the number of participants for each attention check
+attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
+attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
+attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
 ```
@@
 
-lm1 <- lm(veracity ~ newstype + newstype*condition, data = pennys2r1longa2)
+lm1 <- lm(measurement ~ headlineveracity + headlineveracity*condition, data = pennys2r1long_nona)
 summary(lm1)
@@
 
-pennystudy2plot1 <- pennys2r1long %>%
-  select (c(1, 2, 3, 4))
-
 #Find out the sum for each type of news in different condition
 
-p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, na.rm = TRUE, FUN = sum)
-p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))
+p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
 
-##double check for correctness
-sum(pennystudy2plot1$measurement,na.rm = TRUE)
+#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
+p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
 
-#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
-ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
+#plot the graph
+
+ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
   geom_bar(stat = 'identity',position = 'dodge') + 

### 2021-08-05 msc dissertation code.Rmd
latest

@@
 
-pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
 pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
@@
 
-###find out the number of participants for each attention check
+###find out the number of participants (obs) for each attention check level
 attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
@@
 cohen.d(pennys2r1a2cohent$condition, pennys2r1a2cohent$measurement, na.rm = TRUE)
+
+## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
+glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm1 <- glm(measurement ~ condition, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm2 <- glm(measurement ~ condition + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm3 <- glm(measurement ~ condition + attentioncheck + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm4 <- glm(measurement ~ condition + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+anova(glm0,glm1,glm2,glm3,glm4,test='LR')
+
+##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
+summary(glm6)
+
+glm5 <- glm(measurement ~ attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+glm6 <- glm(measurement ~ headlineveracity + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+summary(glm7)
+
+##maybe a mixed effect models?
+#create a new column that recode item number from fake to real to 1-30, with 1-15 indicate fake, 16-30 indicate real
+
+pennys2r1long <- within(pennys2r1long,{
+  item_id <- NA
+  item_id[newstype == "Fake1_1"] <- 1
+  item_id[newstype == "Fake1_2"] <- 2
+  item_id[newstype == "Fake1_3"] <- 3
+  item_id[newstype == "Fake1_4"] <- 4
+  item_id[newstype == "Fake1_5"] <- 5
+  item_id[newstype == "Fake1_6"] <- 6
+  item_id[newstype == "Fake1_7"] <- 7
+  item_id[newstype == "Fake1_8"] <- 8
+  item_id[newstype == "Fake1_9"] <- 9
+  item_id[newstype == "Fake1_10"] <- 10
+  item_id[newstype == "Fake1_11"] <- 11
+  item_id[newstype == "Fake1_12"] <- 12
+  item_id[newstype == "Fake1_13"] <- 13
+  item_id[newstype == "Fake1_14"] <- 14
+  item_id[newstype == "Fake1_15"] <- 15
+  item_id[newstype == "Real1_1"] <- 16
+  item_id[newstype == "Real1_2"] <- 17
+  item_id[newstype == "Real1_3"] <- 18
+  item_id[newstype == "Real1_4"] <- 19
+  item_id[newstype == "Real1_5"] <- 20
+  item_id[newstype == "Real1_6"] <- 21
+  item_id[newstype == "Real1_7"] <- 22
+  item_id[newstype == "Real1_8"] <- 23
+  item_id[newstype == "Real1_9"] <- 24
+  item_id[newstype == "Real1_10"] <- 25
+  item_id[newstype == "Real1_11"] <- 26
+  item_id[newstype == "Real1_12"] <- 27
+  item_id[newstype == "Real1_13"] <- 28
+  item_id[newstype == "Real1_14"] <- 29
+  item_id[newstype == "Real1_15"] <- 30
+})
+
+library(lme4) 
+library(lmerTest)
+
+#model 1, item_id indicates repeated measurements for each item
+mult1 <- lmer (measurement ~ condition + attentioncheck + headlineveracity + (1|item_id),
+             data = pennys2r1long)
+summary(mult1)
 

### 2021-08-09 msc dissertation code.Rmd
latest

@@
 ###find out the number of participants (obs) for each attention check level
-attention1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
-attention2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
-attention3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
+attention1 <- subset(pennys2r1long_nona, attentioncheck %in% c("1","2","3"))
+attention2 <- subset(pennys2r1long_nona, attentioncheck %in% c("2","3"))
+attention3 <- subset(pennys2r1long_nona, attentioncheck %in% c("3"))
+
+```
+
+## relase I should not dichotomise the scale as it loses info and reduces the power.
+```{r, message=FALSE}
+#recreate a data frame that does not rescale the data to either 0,1 but from 0 to 1,so divided each value by rating = (rating - 1)/5
+
+pennystudy2r1nodi <- pennycook2 %>% 
+  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
+
+#successful screen1 test (result = 2)
+pennystudy2r1nodi['screen1']=pennystudy2r1nodi['screen1_4'] + pennystudy2r1nodi['screen1_7']
+
+#successful screen2 test (result = 2)
+pennystudy2r1nodi['screen2']=pennystudy2r1nodi['screen2_3'] + pennystudy2r1nodi['screen2_5']
+
+#successful screen3 test (result = 3)
+pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3_2,1)
+pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,2)
+pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,4)
+pennystudy2r1nodi['screen3'] = na_if(pennystudy2r1nodi$screen3,5)
+#check if screen 3 successful
+mean(pennystudy2r1nodi$screen3, na.rm = TRUE)
+
+#re-code screen test: replace 2 and 3 to 1
+pennystudy2r1nodi["screen1"][pennystudy2r1nodi["screen1"] == 2] <- 1
+pennystudy2r1nodi["screen2"][pennystudy2r1nodi["screen2"] == 2] <- 1
+pennystudy2r1nodi["screen3"][pennystudy2r1nodi["screen3"] == 3] <- 1
+
+#re-code condition control = 0 treatment = 1
+pennystudy2r1nodi["condition"][pennystudy2r1nodi["condition"] == 1] <- 0
+pennystudy2r1nodi["condition"][pennystudy2r1nodi["condition"] == 2] <- 1
+
+#replace NA to 0 in screen 1,2,3
+
+pennystudy2r1nodi[c("screen1","screen2","screen3")][is.na(pennystudy2r1nodi[c("screen1","screen2","screen3")])] <- 0
+
+#create dummy column, add screen 1,2,3 together. Screen = 3 indicate success in all attention check
+pennystudy2r1nodi['dummycheck']=pennystudy2r1nodi['screen1'] + pennystudy2r1nodi['screen2'] + pennystudy2r1nodi['screen3']
+
+#like the researcher did, change data frame from wide to long
+##first drop unnecessary column
+colnames(pennystudy2r1nodi)
+
+pennys2r1longnodi <- subset(pennystudy2r1nodi, select = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,43))
+
+##Add ID column
+pennys2r1longnodi <- tibble::rowid_to_column(pennys2r1longnodi, "ID")
+
+## change from wide to long
+library(tidyr)
+
+keycol <- "newstype"
+valuecol <- "measurement"
+gathercols <- c("Fake1_1","Fake1_2","Fake1_3","Fake1_4","Fake1_5","Fake1_6","Fake1_7","Fake1_8","Fake1_9","Fake1_10","Fake1_11","Fake1_12","Fake1_13","Fake1_14","Fake1_15","Real1_1","Real1_2","Real1_3","Real1_4","Real1_5","Real1_6","Real1_7","Real1_8","Real1_9","Real1_10","Real1_11","Real1_12","Real1_13","Real1_14","Real1_15")
+
+pennys2r1longnodi <- gather_(pennys2r1longnodi, keycol, valuecol, gathercols)
+
+##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one
+
+merge(pennystudy2r1nodi, pennys2r1longnodi, by.x='condition', by.y='ID')
+
+##organize data by ID, then reorder the column
+pennys2r1longnodi <- pennys2r1longnodi[order(pennys2r1longnodi$ID),]
+
+pennys2r1longnodi <- pennys2r1longnodi[, c(1, 2, 7, 8, 6, 5, 4, 3)]
+
+##change dummycheck to attentioncheck to make it clear
+
+names(pennys2r1longnodi)[5] <- "attentioncheck"
+
+##create a headline veracity column, fake news items code as 0, real news items code as 1
+
+pennys2r1longnodi <- pennys2r1longnodi %>%
+  mutate(headlineveracity = case_when(
+    startsWith(newstype, "R") ~ "1",
+    startsWith(newstype, "F") ~ "0"
+    ))
+
+##recode the measurement column
+
+pennys2r1longnodi <- transform(pennys2r1longnodi, rescale = ave(measurement, condition, FUN = function(x) paste0((x-1)/5)))
+
+##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627
+
+pennys2r1longnodi_nona <- pennys2r1longnodi[!is.na(pennys2r1longnodi$measurement),]
+
+attention1nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("1","2","3"))
+attention2nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("2","3"))
+attention3nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("3"))
+
 ```
@@
 
-lm1 <- lm(measurement ~ headlineveracity + headlineveracity*condition, data = pennys2r1long_nona)
+lm1 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = pennys2r1longnodi_nona)
 summary(lm1)
@@
 
-pennys2r1a2cohen <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
-pennys2r1a2cohenc <- subset(pennys2r1a2cohen, condition %in% c("0"))
-pennys2r1a2cohent <- subset(pennys2r1a2cohen, condition %in% c("1"))
+##change headlineveracity and rescale to numeric
+pennys2r1longnodi_nona <- transform(pennys2r1longnodi_nona, 
+                   headlineveracity = as.numeric(headlineveracity),
+                   rescale = as.numeric(rescale))
 
-cohen.d(pennys2r1a2cohenc$Fake, pennys2r1a2cohenc$Real, na.rm = TRUE)
-cohen.d(pennys2r1a2cohent$Fake, pennys2r1a2cohent$Real, na.rm = TRUE)
+sapply(pennys2r1longnodi_nona,mode)
+
+pennys2nodicohenc <- subset(pennys2r1longnodi_nona, condition %in% c("0"))
+pennys2nodicohent <- subset(pennys2r1longnodi_nona, condition %in% c("1"))
 
 #condition vs measurement
+cohen.d(pennys2nodicohent$Real,pennys2nodicohent$Fake, na.rm = TRUE)
+cohen.d(pennys2nodicohenc$Real,pennys2nodicohenc$Fake, na.rm = TRUE)
 
-pennys2r1a2cohenc <- subset(pennys2r1longa2, condition %in% c("0"))
-pennys2r1a2cohent <- subset(pennys2r1longa2, condition %in% c("1"))
+#attention1nodi
+lm2 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention1nodi)
+summary(lm2)
 
-cohen.d(pennys2r1a2cohenc$condition, pennys2r1a2cohenc$measurement, na.rm = TRUE)
-cohen.d(pennys2r1a2cohent$condition, pennys2r1a2cohent$measurement, na.rm = TRUE)
+stargazer(lm2, type='text')
 
+#attention2nodi
+lm3 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention2nodi)
+summary(lm3)
+
+stargazer(lm3, type='text')
+
+#attention3nodi
+lm4 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention3nodi)
+summary(lm4)
+
+stargazer(lm4, type='text')
+
+```
+
+##Try something new, see if it makes the results better
+```{r, message=FALSE}
 ## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
@@
 
-glm2 <- glm(measurement ~ condition + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
+glm2 <- glm(measurement ~ condition + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
 
-glm3 <- glm(measurement ~ condition + attentioncheck + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+glm3 <- glm(measurement ~ condition + condition*headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
 
-glm4 <- glm(measurement ~ condition + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+glm4 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
 
-anova(glm0,glm1,glm2,glm3,glm4,test='LR')
+anova(glm0,glm1,glm2,glm3,test='LR')
 
 ##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
-summary(glm6)
+summary(glm4)
 
-glm5 <- glm(measurement ~ attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
-glm6 <- glm(measurement ~ headlineveracity + attentioncheck +condition* headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+exp(cbind(OR = coef(glm3), confint(glm3)))
 
-summary(glm7)
+glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
+glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))
 
+summary(glm41)
+summary(glm411)
+
+glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
+glm421 <- glm(measurement ~ condition + condition*headlineveracity, data = attention2, family = binomial(link = "logit"))
+
+summary(glm42)
+summary(glm421)
+
+glm43 <- glm(measurement ~ condition + headlineveracity, data = attention3, family = binomial(link = "logit"))
+glm431 <- glm(measurement ~ condition + condition*headlineveracity, data = attention3, family = binomial(link = "logit"))
+
+summary(glm43)
+summary(glm431)
+
+#Additional
 ##maybe a mixed effect models?
-#create a new column that recode item number from fake to real to 1-30, with 1-15 indicate fake, 16-30 indicate real
+
+###create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items
 
@@
 #model 1, item_id indicates repeated measurements for each item
-mult1 <- lmer (measurement ~ condition + attentioncheck + headlineveracity + (1|item_id),
+mult1 <- lmer (measurement ~ condition + condition*headlineveracity + (1|item_id),
              data = pennys2r1long)
@@
 
-### graph 1: including all
+### graph: including all
 ```{r, message=FALSE}
@@
 library(ggplot2)
-
-#Since the plot not specify which condition they use, then I need to plot all 4 graph in different condition
-
-#condition 1: all
 
@@
 ```
+
+### Test (irrelevant)
+
 ### graph 2 attention check above and equal to 1

### 2021-08-10 msc dissertation code.Rmd
latest

@@
 
-#re-code condition control = 0 treatment = 1
-pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
-pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1
-
 #replace NA to 0 in screen 1,2,3
@@
 pennystudy2r1['dummycheck']=pennystudy2r1['screen1'] + pennystudy2r1['screen2'] + pennystudy2r1['screen3']
+
+#re-code condition control = 0 treatment = 1
+pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
+pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1
 
@@
 
-##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one
+##no idea why it doesn't show condition column (control vs treatment) so I merge original condition to the new one
 
@@
 
-##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one
+##no idea why it doesn't show conditions (control vs treatment) so I merge original condition to the new one
 
@@
 glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
-glm421 <- glm(measurement ~ condition + condition*headlineveracity, data = attention2, family = binomial(link = "logit"))
+glm421 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
 
@@
 
-ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
+ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
   geom_bar(stat = 'identity',position = 'dodge') + 
   geom_text(
-    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
+  xlab("Condition") + 
+  ylab("Likelihood of Sharing (%)") +
+  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
+  scale_fill_discrete(name = "Headline Veracity", labels = c("Fake", "Real"))
+
 ```

### 2021-08-11 msc dissertation code.Rmd
with ordinal

@@
 
+##create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items
+
+pennys2r1longnodi_nona <- within(pennys2r1longnodi_nona,{
+  item_id <- NA
+  item_id[newstype == "Fake1_1"] <- 1
+  item_id[newstype == "Fake1_2"] <- 2
+  item_id[newstype == "Fake1_3"] <- 3
+  item_id[newstype == "Fake1_4"] <- 4
+  item_id[newstype == "Fake1_5"] <- 5
+  item_id[newstype == "Fake1_6"] <- 6
+  item_id[newstype == "Fake1_7"] <- 7
+  item_id[newstype == "Fake1_8"] <- 8
+  item_id[newstype == "Fake1_9"] <- 9
+  item_id[newstype == "Fake1_10"] <- 10
+  item_id[newstype == "Fake1_11"] <- 11
+  item_id[newstype == "Fake1_12"] <- 12
+  item_id[newstype == "Fake1_13"] <- 13
+  item_id[newstype == "Fake1_14"] <- 14
+  item_id[newstype == "Fake1_15"] <- 15
+  item_id[newstype == "Real1_1"] <- 16
+  item_id[newstype == "Real1_2"] <- 17
+  item_id[newstype == "Real1_3"] <- 18
+  item_id[newstype == "Real1_4"] <- 19
+  item_id[newstype == "Real1_5"] <- 20
+  item_id[newstype == "Real1_6"] <- 21
+  item_id[newstype == "Real1_7"] <- 22
+  item_id[newstype == "Real1_8"] <- 23
+  item_id[newstype == "Real1_9"] <- 24
+  item_id[newstype == "Real1_10"] <- 25
+  item_id[newstype == "Real1_11"] <- 26
+  item_id[newstype == "Real1_12"] <- 27
+  item_id[newstype == "Real1_13"] <- 28
+  item_id[newstype == "Real1_14"] <- 29
+  item_id[newstype == "Real1_15"] <- 30
+})
+
 ##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627
@@
 ```{r, message=FALSE}
-install.packages("sandwich") 
-install.packages("stargazer")
-install.packages("lmtest")
 library(lmtest)
@@
 
-coeftest(lm1, vcovHC)
-
-#z scored
-scale(pennystudy2r1$Discern)
+coeftest(lm1, vcov = vcovCL, cluster = ~ ID + item_id)
 
@@
 
-#attention1nodi
+#Robustness for different levels of attentiveness
+##attention above 1
 lm2 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention1nodi)
@@
 
-#attention2nodi
+coeftest(lm2, vcov = vcovCL, cluster = ~ ID + item_id)
+
+##attention above 2
 lm3 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention2nodi)
@@
 
-#attention3nodi
+coeftest(lm3, vcov = vcovCL, cluster = ~ ID + item_id)
+
+##attention all 3
 lm4 <- lm(rescale ~ headlineveracity + headlineveracity*condition, data = attention3nodi)
@@
 stargazer(lm4, type='text')
+
+coeftest(lm4, vcov = vcovCL, cluster = ~ ID + item_id)
 
@@
 
-anova(glm0,glm1,glm2,glm3,test='LR')
+glm5 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+anova(glm0,glm1,glm2,glm3,glm4,test='LR')
 
 ##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
-summary(glm4)
+summary(glm5)
+
+###odds ratios and 95% CI
 
@@
 
+## Different attention check group
 glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
@@
 summary(glm431)
+
+#Ordinal logistic regression
+
+install.packages("ordinal")
+install.packages("ggeffects")
+
+library(ordinal)
+library(ggeffects)
+
+ordinaldata <- pennys2r1longnodi_nona
+
+str(ordinaldata)
+ordinaldata$measurement <- as.factor(ordinaldata$measurement)
+
+ordinal <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata, link = "logit")
+
+summary(ordinal)
+
+exp(coef(ordinal))
+
+ggpredict_ordinal <- ggpredict(ordinal, terms = c("condition","headlineveracity"))
+ggpredict_ordinaldata = data.frame(ggpredict_ordinal)
+
+ggpredict_ordinal
+str(ggpredict_ordinaldata)
+
+ggpredict_ordinaldata$x = factor(ggpredict_ordinaldata$x)
+levels(ggpredict_ordinaldata$x) = c("False", "True")
+colnames(ggpredict_ordinaldata)[c(1, 5,6)] =c("Headlineveracity", "Rating", "group")
+levels(ggpredict_ordinaldata$group) = c("Control", "Treatment")
+ggpredict_ordinaldata
+
+ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + theme_minimal() +facet_wrap(~group)
+
+```
+
+### reproduction of figure 2 without considering attention check
+
+### graph: including all
+```{r, message=FALSE}
+
+library(ggplot2)
+
+#Find out the sum for each type of news in different condition
+
+p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
+
+#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
+p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
+
+#plot the graph
+
+ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
+  xlab("Condition") + 
+  ylab("Likelihood of Sharing (%)") +
+  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
+  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True"))
+
+```
+
+### Tests (irrelevant)
+
+#z scored
+scale(pennystudy2r1$D)
 
@@
 mult1 <- lmer (measurement ~ condition + condition*headlineveracity + (1|item_id),
-             data = pennys2r1long)
+             data = pennys2r1longnodi_nona)
 summary(mult1)
-
-```
-
-### reproduction of figure 2 without considering attention check
-
-### graph: including all
-```{r, message=FALSE}
-
-library(ggplot2)
-
-#Find out the sum for each type of news in different condition
-
-p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
-
-#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
-p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
-
-#plot the graph
-
-ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
-  geom_bar(stat = 'identity',position = 'dodge') + 
-  geom_text(
-    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
-  xlab("Condition") + 
-  ylab("Likelihood of Sharing (%)") +
-  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
-  scale_fill_discrete(name = "Headline Veracity", labels = c("Fake", "Real"))
-
-```
-
-### Test (irrelevant)
 

### 2021-08-11 msc dissertation code.Rmd
latest

@@
 
+## reproduction of figure 2 without considering attention check
+
+### graph: including all
+```{r, message=FALSE}
+
+library(ggplot2)
+
+#Find out the sum for each type of news in different condition
+
+p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
+
+#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
+p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
+
+#plot the graph
+
+ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
+  xlab("Condition") + 
+  ylab("Likelihood of Sharing (%)") +
+  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
+  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True")) + labs(title = "All Subjects")
+
+ggsave("All Subjects bar chart.png")
+```
+
 ##Try something new, see if it makes the results better
+###GLM
 ```{r, message=FALSE}
@@
 summary(glm431)
+```
 
+###Ordinal logistic regression
+```{r, message=FALSE}
 #Ordinal logistic regression
@@
 install.packages("ggeffects")
+install.packages("ggrepel")
 
@@
 library(ggeffects)
+library(ggrepel)
 
+## All subjects
 ordinaldata <- pennys2r1longnodi_nona
@@
 levels(ggpredict_ordinaldata$x) = c("False", "True")
-colnames(ggpredict_ordinaldata)[c(1, 5,6)] =c("Headlineveracity", "Rating", "group")
+colnames(ggpredict_ordinaldata)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
 levels(ggpredict_ordinaldata$group) = c("Control", "Treatment")
@@
 
-ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + theme_minimal() +facet_wrap(~group)
+ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
+  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + 
+  geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All Subjects")
 
-```
+ggsave("All Subjects.png")
 
-### reproduction of figure 2 without considering attention check
+## attention check1
 
-### graph: including all
-```{r, message=FALSE}
+ordinaldata1 <- attention1nodi
 
-library(ggplot2)
+str(ordinaldata1)
+ordinaldata1$measurement <- as.factor(ordinaldata1$measurement)
 
-#Find out the sum for each type of news in different condition
+ordinal1 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata1, link = "logit")
 
-p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
+summary(ordinal1)
 
-#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
-p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
+exp(coef(ordinal1))
 
-#plot the graph
+ggpredict_ordinal1 <- ggpredict(ordinal1, terms = c("condition","headlineveracity"))
+ggpredict_ordinaldata1 = data.frame(ggpredict_ordinal1)
 
-ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
-  geom_bar(stat = 'identity',position = 'dodge') + 
-  geom_text(
-    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
-  xlab("Condition") + 
-  ylab("Likelihood of Sharing (%)") +
-  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
-  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True"))
+ggpredict_ordinal1
+str(ggpredict_ordinaldata1)
+
+ggpredict_ordinaldata1$x = factor(ggpredict_ordinaldata1$x)
+levels(ggpredict_ordinaldata1$x) = c("False", "True")
+colnames(ggpredict_ordinaldata1)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
+levels(ggpredict_ordinaldata1$group) = c("Control", "Treatment")
+ggpredict_ordinaldata1
+
+ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
+  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 1 Screener Correct")
+
+ggsave("\u2265 1 Screener Correct.png")
+
+##tips, \u2265 could display greater and equal to sign
+
+## attention check2
+
+ordinaldata2 <- attention2nodi
+
+str(ordinaldata2)
+ordinaldata2$measurement <- as.factor(ordinaldata2$measurement)
+
+ordinal2 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata2, link = "logit")
+
+summary(ordinal2)
+
+exp(coef(ordinal2))
+
+ggpredict_ordinal2 <- ggpredict(ordinal2, terms = c("condition","headlineveracity"))
+ggpredict_ordinaldata2 = data.frame(ggpredict_ordinal2)
+
+ggpredict_ordinal2
+str(ggpredict_ordinaldata2)
+
+ggpredict_ordinaldata2$x = factor(ggpredict_ordinaldata2$x)
+levels(ggpredict_ordinaldata2$x) = c("False", "True")
+colnames(ggpredict_ordinaldata2)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
+levels(ggpredict_ordinaldata2$group) = c("Control", "Treatment")
+ggpredict_ordinaldata2
+
+ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
+  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 2 Screener Correct")
+
+ggsave("\u2265 2 Screener Correct.png")
+
+## attention check 3
+
+ordinaldata3 <- attention3nodi
+
+str(ordinaldata3)
+ordinaldata3$measurement <- as.factor(ordinaldata3$measurement)
+
+ordinal3 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata3, link = "logit")
+
+summary(ordinal3)
+
+exp(coef(ordinal3))
+
+ggpredict_ordinal3 <- ggpredict(ordinal3, terms = c("condition","headlineveracity"))
+ggpredict_ordinaldata3 = data.frame(ggpredict_ordinal3)
+
+ggpredict_ordinal3
+str(ggpredict_ordinaldata3)
+
+ggpredict_ordinaldata3$x = factor(ggpredict_ordinaldata3$x)
+levels(ggpredict_ordinaldata3$x) = c("False", "True")
+colnames(ggpredict_ordinaldata3)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
+levels(ggpredict_ordinaldata3$group) = c("Control", "Treatment")
+ggpredict_ordinaldata3
+
+ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
+  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All 3 Screener Correct")
+
+ggsave("All 3 Screener Correct.png")
 

### 2021-08-13 msc dissertation code.Rmd
latest

@@
 title: "msc dissertation"
-author: "Halleyson Li"
-date: "'r Sys.Date()'"
-output: html_document
+author: "Halleyson Li 200256823"
+date: '''r Sys.Date()'''
+output:
+  html_document: default
+  pdf_document: default
 line-citations: apalike
@@
 
+Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file.
+But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv but not read.csv.
+
 ```{r, message=FALSE}
@@
 
-pennycook2 <- read_csv("Pennycook et al._Study 2.csv")
+pennycook2 <- read_csv("Pennycooketal Study 2.csv")
+
 # Quick check
 head(pennycook2)
-
 ```
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, results='hide'}
 
@@
 pennystudy2r1 <- pennycook2 %>% 
-  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
+  dplyr::select(c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
 
 #re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
+###(06/08/21 update: realize I could do it after change it from wide to long, then only the column: "measurement" needs to perform the change.)
 
@@
 
-###find out the number of participants (obs) for each attention check level
-attention1 <- subset(pennys2r1long_nona, attentioncheck %in% c("1","2","3"))
-attention2 <- subset(pennys2r1long_nona, attentioncheck %in% c("2","3"))
-attention3 <- subset(pennys2r1long_nona, attentioncheck %in% c("3"))
+###find out the number of participants (obs) for each attention check level (use it to compare with No of participants in Table S5).
+
+No.participantsa1 <- subset(pennystudy2r1, dummycheck %in% c("1","2","3"))
+No.participantsa2 <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
+No.participantsa3 <- subset(pennystudy2r1, dummycheck %in% c("3"))
 
@@
 ## relase I should not dichotomise the scale as it loses info and reduces the power.
-```{r, message=FALSE}
+```{r, message=FALSE, results='hide'}
 #recreate a data frame that does not rescale the data to either 0,1 but from 0 to 1,so divided each value by rating = (rating - 1)/5
@@
 pennystudy2r1nodi <- pennycook2 %>% 
-  select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
+ dplyr::select (c(1, 210, 211, 212, 213, 214, 215, 216, 217, 218, 219, 220, 221, 222, 223, 224, 225, 226, 227, 228, 229, 230, 231, 232, 233, 234, 235, 236, 237, 238, 239, 2, 3, 4, 57, 60, 250, 252, 284,))
 
@@
 
-##no idea why it doesn't show conditions (control vs treatment) so I merge original condition to the new one
+## I merge original condition to the new one
 
@@
 
-##create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items
+##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627
+
+pennys2r1longnodi_nona <- pennys2r1longnodi[!is.na(pennys2r1longnodi$measurement),]
+
+##create a new column that recode item number from fake and real to 1-30, with 1-15 indicate each fake items, 16-30 indicate each real items, need it for clustering robust standard errors.
 
@@
   item_id[newstype == "Real1_14"] <- 29
-  item_id[newstype == "Real1_15"] <- 30
-})
+  item_id[newstype == "Real1_15"] <- 30})
 
-##realise that original researcher exclude the observation with answer contains na, thus the obs needs to minus 23 to match original obs 25,627
-
-pennys2r1longnodi_nona <- pennys2r1longnodi[!is.na(pennys2r1longnodi$measurement),]
-
+##subset based on attetnion check
 attention1nodi <- subset(pennys2r1longnodi_nona, attentioncheck %in% c("1","2","3"))
@@
 
-install.packages("effsize")
 library(effsize)
@@
 
+#check the class
 sapply(pennys2r1longnodi_nona,mode)
 
+#subset the table based on condition
 pennys2nodicohenc <- subset(pennys2r1longnodi_nona, condition %in% c("0"))
@@
 
-#condition vs measurement
+#condition vs measurement effect size, using participants' average measurement.
 cohen.d(pennys2nodicohent$Real,pennys2nodicohent$Fake, na.rm = TRUE)
@@
 
-## reproduction of figure 2 without considering attention check
+## reproduction of figure 2 (without considering attention check)
 
@@
 library(ggplot2)
+library(DescTools)
 
-#Find out the sum for each type of news in different condition
+#create a table contain mean and CI for each headline veracity in each condition
+z <- with(pennys2r1long_nona, 
+          aggregate(measurement, list(condition, headlineveracity), MeanCI))
+z <- xtabs(x ~ Group.1 + Group.2, z)
 
-p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
+z = data.frame(z)
 
-#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
-p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
+#check the results with equation I know for sure
+dummy <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, FUN = mean)
 
-#plot the graph
+#reshape the graph
+z1 <- subset(z, Var3 %in% c("mean"))
+z2 <- subset(z, Var3 %in% c("lwr.ci"))
+z3 <- subset(z, Var3 %in% c("upr.ci"))
 
-ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
-  geom_bar(stat = 'identity',position = 'dodge') + 
+zsummary <- cbind(z1,z2$Freq,z3$Freq)
+
+zsummary <- zsummary %>% 
+  dplyr::select (c(1, 2, 4, 5, 6))
+
+names(zsummary)[1] <- "condition"
+names(zsummary)[2] <- "headlineveracity"
+names(zsummary)[3] <- "percent"
+names(zsummary)[4] <- "lowci"
+names(zsummary)[5] <- "upci"
+
+#change the value to %
+zsummary$percent <- zsummary$percent*100
+zsummary$lowci <- zsummary$lowci*100
+zsummary$upci <- zsummary$upci*100
+str(zsummary)
+
+#plot the graph with error bar indicate CI
+
+ggplot(zsummary, aes(x = condition, y = percent, fill = forcats::fct_rev(headlineveracity))) + 
+  geom_bar(stat = 'identity',position = 'dodge',width = 0.5) + 
   geom_text(
-    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
+    aes(label = sprintf("%.2f",percent)), vjust = 2.5, position = position_dodge(0.5)) +
   xlab("Condition") + 
@@
   scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
-  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True")) + labs(title = "All Subjects")
+  scale_fill_manual(values = c("orange2","forestgreen"), name = "Headline Veracity", labels = c("True", "False")) + labs(title = "All Subjects") + 
+  geom_errorbar(aes(ymin = lowci, ymax = upci,width = 0.2),position = position_dodge(0.5), size = 0.6)
+
+##tips: forcats::fct_rev() is to reverse the order, use scale_fill_manual(values = to change colour
 
 ggsave("All Subjects bar chart.png")
+
 ```
@@
 ##Try something new, see if it makes the results better
-###GLM
-```{r, message=FALSE}
-## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
-glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))
 
-glm1 <- glm(measurement ~ condition, data = pennys2r1long_nona, family = binomial(link = "logit"))
-
-glm2 <- glm(measurement ~ condition + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
-
-glm3 <- glm(measurement ~ condition + condition*headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
-
-glm4 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
-
-glm5 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
-
-anova(glm0,glm1,glm2,glm3,glm4,test='LR')
-
-##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
-summary(glm5)
-
-###odds ratios and 95% CI
-
-exp(cbind(OR = coef(glm3), confint(glm3)))
-
-## Different attention check group
-glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
-glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))
-
-summary(glm41)
-summary(glm411)
-
-glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
-glm421 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
-
-summary(glm42)
-summary(glm421)
-
-glm43 <- glm(measurement ~ condition + headlineveracity, data = attention3, family = binomial(link = "logit"))
-glm431 <- glm(measurement ~ condition + condition*headlineveracity, data = attention3, family = binomial(link = "logit"))
-
-summary(glm43)
-summary(glm431)
-```
-
-###Ordinal logistic regression
+###Ordinal logistic regression (best to apply when using likert scale)
 ```{r, message=FALSE}
 #Ordinal logistic regression
-
-install.packages("ordinal")
-install.packages("ggeffects")
-install.packages("ggrepel")
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All 3 Screener Correct")
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5) + labs(title = "All 3 Screener Correct")
 
@@
 
-### Tests (irrelevant)
+### code testing (irrelevant)
 
+###GLM (bad idea, because it dicotomize the results leads to loss information and verlidity)
+
+## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
+glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm1 <- glm(measurement ~ condition, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm2 <- glm(measurement ~ condition + headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm3 <- glm(measurement ~ condition + condition*headlineveracity, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm4 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+glm5 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = pennys2r1long_nona, family = binomial(link = "logit"))
+
+anova(glm0,glm1,glm2,glm3,glm4,test='LR')
+
+##looking at summary glm4, it is cleat that condition does not have a significant effect on measurement
+summary(glm5)
+
+###odds ratios and 95% CI
+
+exp(cbind(OR = coef(glm3), confint(glm3)))
+
+##subset the attention based on attention check
+attention1 <- subset(pennys2r1long_nona, attentioncheck %in% c("1","2","3"))
+attention2 <- subset(pennys2r1long_nona, attentioncheck %in% c("2","3"))
+attention3 <- subset(pennys2r1long_nona, attentioncheck %in% c("3"))
+
+## Different attention check group
+glm41 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention1, family = binomial(link = "logit"))
+glm411 <- glm(measurement ~ condition + condition*headlineveracity, data = attention1, family = binomial(link = "logit"))
+
+summary(glm41)
+summary(glm411)
+
+glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
+glm421 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
+
+summary(glm42)
+summary(glm421)
+
+glm43 <- glm(measurement ~ condition + headlineveracity, data = attention3, family = binomial(link = "logit"))
+glm431 <- glm(measurement ~ condition + condition*headlineveracity, data = attention3, family = binomial(link = "logit"))
+
+summary(glm43)
+summary(glm431)
+```
+
+#old graph
+
+#Find out the sum for each type of news in different condition
+
+p1 <- aggregate(measurement~condition+headlineveracity, data = pennys2r1long_nona, na.rm = TRUE, FUN = sum)
+
+#since the obs is 25,627, thus for each news in each condition, it observed 25,627/4 = 6406.75
+p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/6406.75, 4)*100)))
+
+#plot the graph
+
+ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
+  geom_bar(stat = 'identity',position = 'dodge') + 
+  geom_text(
+    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
+  xlab("Condition") + 
+  ylab("Likelihood of Sharing (%)") +
+  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
+  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True")) + labs(title = "All Subjects")
+
+```
 #z scored
@@
 
-```{r, message=FALSE}
-
 #condition 2: above and equal to 1
@@
 ### graph 3 attention check above and equal to 2
-```{r, message=FALSE}
+
 #condition 3: above and equal to 2
@@
 ### graph 3 attention check above and equal to 2: mean
-```{r, message=FALSE}
+
 #condition 3: above and equal to 2
@@
 ### graph 4 attention check equal to 3
-```{r, message=FALSE}
+
 #condition 3: equal to 3

### 2021-08-20 index.Rmd
latest

--- 2021-08-13 msc dissertation code.Rmd
@@
 title: "msc dissertation"
-author: "Halleyson Li 200256823"
+author: "200256823"
 date: '''r Sys.Date()'''
@@
 Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file.
-But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv but not read.csv.
+But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv, not read.csv.
 
@@
 #re-code sharing intentions (fake/real) using the scale midpoint (1-3 = 0, 4-6 = 1)
-###(06/08/21 update: realize I could do it after change it from wide to long, then only the column: "measurement" needs to perform the change.)
+##(06/08/21 update: realize I could do it after change it from wide to long, then only the column: "measurement" needs to perform the change, for documentation reason, I leave it as it is.)
 
@@
 
-##Try something new, see if it makes the results better
+##Considering the likert scale should be treated as categorical rather than continuse, thus the ordinal logistic regression should be used, rather than normal linear regression
 
-###Ordinal logistic regression (best to apply when using likert scale)
 ```{r, message=FALSE}
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + 
-  geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All Subjects")
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All Subjects")
+
+  + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 1 Screener Correct")
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "\u2265 1 Screener Correct")
+
+ + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 2 Screener Correct")
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing")  + labs(title = "\u2265 2 Screener Correct")
+
+ + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5) + labs(title = "All 3 Screener Correct")
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All 3 Screener Correct")
+
+ + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)
 

### 2021-08-20 index.Rmd
latest

@@
 
-Because the original data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file.
+Because the orginal data was not encoded in UFT-8, so after download the original data, has to open it with excel and re-save it with UFT-8 encoded .csv file.
 But if knit/publish is not required, then this process is not required, but for loading the data (using readr), it has to be read_csv, not read.csv.

### 2021-08-24 index.Rmd
latest

@@
 
+#rename the columns for make it clear
+
 names(zsummary)[1] <- "condition"
@@
   scale_fill_manual(values = c("orange2","forestgreen"), name = "Headline Veracity", labels = c("True", "False")) + labs(title = "All Subjects") + 
-  geom_errorbar(aes(ymin = lowci, ymax = upci,width = 0.2),position = position_dodge(0.5), size = 0.6)
+  geom_errorbar(aes(ymin = lowci, ymax = upci,width = 0.2),position = position_dodge(0.5), size = 0.6) + 
+  theme( axis.title.x = element_text(size=14, face="bold"),
+axis.title.y = element_text( size=14, face="bold"), axis.text.x = element_text(size = 14, face="bold"),axis.text.y = element_text(size = 14, face="bold"))
 
@@
 #Ordinal logistic regression
-
 library(ordinal)
@@
 
+#change measurement to factor
 str(ordinaldata)
@@
 
-ordinal <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata, link = "logit")
+#model equation
+ordinal <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata, link = "logit")
 
@@
 exp(coef(ordinal))
+
+#ggpredict change log odds to probabilities
 
@@
 
+#plot the graph
 ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All Subjects")
-
-  + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "All Subjects") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points
 
@@
 
-ordinal1 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata1, link = "logit")
+ordinal1 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata1, link = "logit")
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "\u2265 1 Screener Correct")
-
- + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "\u2265 1 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
 
@@
 
-ordinal2 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata2, link = "logit")
+ordinal2 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata2, link = "logit")
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing")  + labs(title = "\u2265 2 Screener Correct")
-
- + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating")  + labs(title = "\u2265 2 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)
 
@@
 
-ordinal3 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata3, link = "logit")
+ordinal3 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata3, link = "logit")
 
@@
   geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) +
-  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All 3 Screener Correct")
-
- + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)
+  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "All 3 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)
 
